Appendix

### 2025-10-17 manuscript_rmarkdown/manuscript_appendix.Rmd
Update ranking results for Box-Cox transformations.

```
\begin{table}
\begin{center}
\caption{
Comparison of average rank between Box-Cox transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 10000 sequences each. The clean dataset consists of sequences derived through inverse Box-Cox transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
If necessary, each sequence was shifted so that every element had a strictly positive value. 
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_box_cox}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         7.65  &         6.96  &         7.28  &         6.58  &         7.45  &         6.78 \\
conventional                          & &         3.10  &         5.98  &         5.42  &         6.16  &         6.49  &         6.10 \\
conventional (z-score norm.)          & &         4.19  &         6.28  &         4.85  &         6.33  &         4.38  &         5.85 \\
conventional (robust scaling)         & &         4.20  &         6.28  &         4.78  &         6.33  &         4.30  &         5.86 \\
Raymaekers-Rousseeuw                  & &         4.46  &         3.55  &         5.39  &         3.69  &         6.29  &         5.84 \\ 
Raymaekers-Rousseeuw (z-score norm.)  & &         6.21  &         3.83  &         4.95  &         3.85  &         4.51  &         3.50 \\ 
Raymaekers-Rousseeuw (robust scaling) & &         6.12  &         3.82  &         4.97  &         3.85  &         4.52  &         3.50 \\
invariant                             & & \textbf{2.99} &         5.55  & \textbf{3.65} &         6.01  & \textbf{3.52} &         5.57 \\
robust invariant                      & &         6.09  & \textbf{2.75} &         3.71  & \textbf{2.20} &         3.55  & \textbf{2.00} \\

>>>>

```
\begin{table}
\begin{center}
\caption{
Comparison of average rank between Box-Cox transformation methods based on either residual error (without outliers) or residual error of the central portion
(with outliers; $\kappa = 0.80$) over 3 datasets with 100000 sequences each. The clean dataset consists of sequences derived through inverse Box-Cox transformation
of data sampled from a standard normal distribution. The dirty dataset contains sequences sampled from asymmetric generalised normal distributions.
The shifted dataset also contains sequences sampled from asymmetric generalised normal distributions, but centred at 100, and scaled by 0.001.
If necessary, each sequence was shifted so that every element had a strictly positive value. 
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
A rank of 1 is the best and a rank of 9 the worst. For each dataset, the best ranking transformation is marked in bold.
}
\label{tab:comparison_methods_simulations_box_cox}
\begin{tabular}{l | l r r r r r r}

@@

none                                  & &         7.63  &         6.95  &         7.29  &         6.59  &         7.47  &         6.78 \\
conventional                          & &         3.11  &         5.98  &         5.41  &         6.18  &         6.51  &         6.10 \\
conventional (z-score norm.)          & &         4.15  &         6.27  &         4.83  &         6.32  &         4.34  &         5.84 \\
conventional (robust scaling)         & &         4.20  &         6.29  &         4.84  &         6.31  &         4.35  &         5.84 \\
Raymaekers-Rousseeuw                  & &         4.50  &         3.56  &         5.39  &         3.69  &         6.30  &         5.80 \\ 
Raymaekers-Rousseeuw (z-score norm.)  & &         6.23  &         3.80  &         4.93  &         3.85  &         4.48  &         3.50 \\ 
Raymaekers-Rousseeuw (robust scaling) & &         6.12  &         3.80  &         4.99  &         3.87  &         4.53  &         3.51 \\
invariant                             & & \textbf{2.96} &         5.59  & \textbf{3.62} &         6.01  & \textbf{3.51} &         5.58 \\
robust invariant                      & &         6.10  & \textbf{2.76} &         3.68  & \textbf{2.19} & \textbf{3.51} & \textbf{2.00} \\
